---
title: "French public discourse collection"
title-block-banner: true
subtitle: "Scrap eveything"
author:
  - name: Olivier Caron
    email: olivier.caron@dauphine.psl.eu
    affiliations: 
      name: "Paris Dauphine - PSL"
      city: Paris
      state: France
date : "12/18/2023"
toc: true
number-sections: true
number-depth: 10
format:
  html:
    theme:
      light: litera
      #dark: darkly
    code-fold: true
    code-summary: "Display code"
    code-tools: true #enables to display/hide all blocks of code
    code-copy: true #enables to copy code
    grid:
      body-width: 1000px
      margin-width: 100px
    toc: true
    toc-title: "Table of content"
    toc-location: left
execute:
  echo: true
  warning: false
  message: false
editor: visual
fig-align: "center"
highlight-style: ayu
reference-location: margin
---

```{r}
#| label: libraries-r

library(tidyverse)
library(data.table)
library(microbenchmark)
library(DT)
library(ggthemes)
library(ggthemr)
library(flextable)
```

```{r}
#| label: data-loading-r

ggthemr('dust')

df_combined <- fread("data/combined_data_VF2.csv") %>%
  mutate_all(~ifelse(. == "", NA, .)) %>%
  mutate(page_number = as.integer(page_number)) %>%
  arrange(page_number)

```

## French public discourse collection

### What is it ?

La Collection des discours publics, which translates to "The Collection of Public Speeches" in English, gathers more than 160,000 speeches delivered by key figures in French public life. This includes speeches by the President of the Republic since 1974, the Prime Minister and government members since the early 1980s, and communiqués from the Council of Ministers since 1974, among others.

[Link to website](https://www.vie-publique.fr/discours?page=0 "French public discourse")

## Scraping process

The initial attempt was made using the **`rvest`** package, which I had previous experience with. However, I encountered an issue with undetected JavaScript that hindered the scraping process. Consequently, I switched to simulating normal human browsing behavior using Selenium, a technique I learnt in a [PSL](https://psl.eu/ "PSL website") course last year, taught by [Bruno Chaves](https://acss-dig.psl.eu/fr/equipe/bruno-chaves-ferreira "Bruno Chaves ACSS website").

This approach proved to be very effective. I also happened to have a sample code using this module, so I decided to proceed with it. In the GitHub repository, the **`scrapping_python.ipynb`** notebook was used to scrape various pages of the website.

As this process was somewhat time-consuming and too long to bear, I explored different methods to accelerate the process and successfully implemented multithreading using Python's [concurrent.futures module](#0), significantly enhancing the speed of the scraping operation.

The relevant code can be found in the **`multithreading_scrapping.ipynb`** notebook.

## Verify missing dates

Put the page numbers where the date is missing into a .txt file, each on a new line.

The challenge is that the CSS selector varies from page to page; sometimes, there is a "time" tag, sometimes, just a HTML `<p>` paragraph.

We do this to loop through them and retrieve the dates.

```{r}
#| label: verify-missing-dates

df_no_date2 <- df_combined %>% 
  filter(date == "" | is.na(date)) %>%
  select(page_number) %>%
  distinct()

#write vector to txt file
write.table(df_no_date2, "data/df_no_date2.txt", row.names = FALSE, col.names = FALSE)

```

## Verify missing texts

Place the page numbers where the text is missing into a `.txt file` in the `data\` folder, each on a new line.

The challenge is that the CSS selector varies from page to page; sometimes it's an 'integral text', other times it's a 'resume text'.

We do this to loop through the pages and retrieve the texts.

```{r}
#| label: verify-missing-texts

df_no_text <- df_combined %>% 
  filter(text == "" | is.na(text)) %>%
  select(page_number) %>%
  distinct()

#write vector to txt file
write.table(df_no_text, "data/df_no_text.txt", row.names = FALSE, col.names = FALSE)


```

## Remove false keywords

When I wrote the first scrapping script, I browsed a few pages to find similarities and difference between the pages. I noticed that it was easy to get the keywords with the `fr-tag fr-tag--green-emeraude` class.

The problem is that this class is also used for the tag of each discourse. I've also noticed that multiple tags can be assigned to a single discourse. **I only kept the first one so this can be modified for future work**.

What is left to do now is removing the keywords that are actually tags, which means removing the first keyword of each discourse and the ";" that follows.

```{r}
#| label: remove-false-keywords

df_combined <- df_combined %>%
  mutate(keywords = stringr::str_replace(keywords, "^[^;]+\\s*;\\s*", ""))

write_csv(df_combined, "data/combined_data_final_version.csv")

```

## Benchmarks for reading csv files

### fread vs read.csv vs read_csv vs vroom

I processed a total of 12,348 CSV files, which were read and concatenated into a single large CSV file using the [Polars library in Python](https://pola.rs/ "polars library in Python").

The primary objective here is to evaluate the efficiency of various libraries in R in terms of the time they take to read this consolidated CSV file, which is approximately 1.2 GB in size.

This will help me for future work.

```{r}
#| label: quick-benchmark2
#| column: screen-inset-right
#| fig-width: 13

benchmark_results <- microbenchmark(
  df_combined <- fread("data/combined_data_final_version.csv"),
  df_combined <- read.csv("data/combined_data_final_version.csv"),
  df_combined <- read_csv("data/combined_data_final_version.csv"),
  df_combined <- vroom::vroom("data/combined_data_final_version.csv"),
  times = 5
)

benchmark_results <- benchmark_results %>%
  mutate(time = time / 1e9)

ggplot(benchmark_results) +
  aes(x = expr, y = time, fill = expr) +
  geom_violin(adjust = 0.7, scale = "width") +
  coord_flip() +
  theme(legend.position = "none")+
  ylab("Time (s)")+
  xlab("")
```

It seems like the [vroom package](https://www.tidyverse.org/blog/2019/05/vroom-1-0-0/ "vroom package website") is the fastest. However, I had some problems with the "media" column with vroom, so I'll stick with `fread`.

By the way, the results of the [microbenchmark](https://www.rdocumentation.org/packages/microbenchmark/versions/1.4.10/topics/microbenchmark "microbenchmark r package website") package are as follows:\

```{r}
#| label: microbenchmark-results
#| column: screen-inset-right
#| tbl-cap: Microbenchmark results

summary(benchmark_results) %>%
  as.data.frame() %>%
  mutate(across(-1, ~round(.,2))) %>%
  flextable::flextable() %>%
  flextable::theme_box() %>%
  flextable::autofit()
```

### Change number of threads fread

```{r}
#| label: quick-benchmark
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 6

#load library to detect number of cores
library(parallel)
cat("Number of cores:", detectCores())

benchmark_results <- microbenchmark(
  df_combined <- fread("data/combined_data_final_version.csv"),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 22),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 20),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 18),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 16),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 14),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 12),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 10),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 8),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 6),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 4),
  df_combined <- fread("data/combined_data_final_version.csv", nThread = 2),
  times = 5
)

#benchmark_results <- benchmark_results %>%
  #mutate(time = time / 1e9)


#ggplot(benchmark_results) +
  #aes(x = expr, y = time, fill = expr) +
  #geom_violin(adjust = 0.7, scale = "width") +
  #coord_flip() +
  #theme(legend.position = "none")+
  #ylab("Time (s)")+
  #xlab("")+
  #theme_minimal()

autoplot(benchmark_results)
```

In conclusion, it appears that specifying the number of threads while using the **`fread`** function is not particularly necessary for a file this size.
