---
title: "French public discourse collection"
title-block-banner: true
subtitle: "Scrap eveything"
author:
  - name: Olivier Caron
    email: olivier.caron@dauphine.psl.eu
    affiliations: 
      name: "Paris Dauphine - PSL"
      city: Paris
      state: France
date : "14/12/2023"
toc: true
number-sections: true
number-depth: 10
format:
  html:
    theme:
      light: litera
      #dark: darkly
    code-fold: true
    code-summary: "Display code"
    code-tools: true #enables to display/hide all blocks of code
    code-copy: true #enables to copy code
    grid:
      body-width: 1000px
      margin-width: 100px
    toc: true
    toc-title: "Table of content"
    toc-location: left
execute:
  echo: true
  warning: false
  message: false
editor: visual
fig-align: "center"
highlight-style: ayu
reference-location: margin
---

```{r}
#| label: data-libraries-r
#| echo: false
#| eval: true

library(tidyverse)
library(data.table)
```

```{python}
#| label: data-libraries-python
#| echo: false
#| eval: true
import polars as pl
import glob
import os
```

## French public discourse collection

### What is it ?

La Collection des discours publics, which translates to "The Collection of Public Speeches" in English, gathers more than 160,000 speeches delivered by key figures in French public life. This includes speeches by the President of the Republic since 1974, the Prime Minister and government members since the early 1980s, and communiqués from the Council of Ministers since 1974, among others.

[Link to website](https://www.vie-publique.fr/discours?page=0 "French public discourse")

## Gather every data

```{r}
#| label: gather-data


df1 <- read.csv("data/csv_page/csv_page_0.csv")
df2 <- read.csv("data/csv_page/csv_page_1999.csv")
```

```{python}
#| label: gather-data-python

import polars as pl
import glob
import os

def combine_csv_files(folder_path):
    """
    Combine all CSV files in a given folder into a single DataFrame using Polars.
    Columns that are not present in all CSV files are filled with None.
    
    :param folder_path: Path to the folder containing CSV files.
    :return: Combined DataFrame.
    """
    # Création du chemin complet pour le motif de recherche des fichiers CSV
    search_pattern = os.path.join(folder_path, "csv_page_*.csv")

    # Recherche de tous les fichiers CSV correspondants
    csv_files = glob.glob(search_pattern)

    # Lecture de tous les fichiers CSV
    dfs = [pl.read_csv(file) for file in csv_files]

    # Combinaison des DataFrames avec la méthode concat et how='diagonal'
    combined_df = pl.concat(dfs, how='diagonal')

    return combined_df

# Chemin du dossier contenant les fichiers CSV
folder_path = "data/csv_page"

# Exécution de la fonction et stockage du DataFrame combiné
combined_dataframe = combine_csv_files(folder_path)

```

```{r}
#| label: gather-data-r

list_of_csv_files <- list.files("data/csv_page")

#check if every csv file exists by looping through the list of files
for (i in list_of_csv_files) {
  file_path <- file.path("data/csv_page", i)
  if (!file.exists(file_path)) {
    print(paste(file_path, "n'existe pas"))
  }
}


```
