---
title: "French public discourse collection"
title-block-banner: true
subtitle: "Scrap eveything"
author:
  - name: Olivier Caron
    email: olivier.caron@dauphine.psl.eu
    affiliations: 
      name: "Paris Dauphine - PSL"
      city: Paris
      state: France
date : "14/12/2023"
toc: true
number-sections: true
number-depth: 10
format:
  html:
    theme:
      light: litera
      #dark: darkly
    code-fold: true
    code-summary: "Display code"
    code-tools: true #enables to display/hide all blocks of code
    code-copy: true #enables to copy code
    grid:
      body-width: 1000px
      margin-width: 100px
    toc: true
    toc-title: "Table of content"
    toc-location: left
execute:
  echo: true
  warning: false
  message: false
editor: visual
fig-align: "center"
highlight-style: ayu
reference-location: margin
---

```{r}
#| label: data-libraries-r
#| echo: false
#| message: false
#| eval: true

library(tidyverse)
library(data.table)
library(microbenchmark)
```

## French public discourse collection

### What is it ?

La Collection des discours publics, which translates to "The Collection of Public Speeches" in English, gathers more than 160,000 speeches delivered by key figures in French public life. This includes speeches by the President of the Republic since 1974, the Prime Minister and government members since the early 1980s, and communiqués from the Council of Ministers since 1974, among others.

[Link to website](https://www.vie-publique.fr/discours?page=0 "French public discourse")

## Verify missing dates
```{r}
#| label: verify-missing-dates

df_no_date2 <- df_combined %>% 
  filter(date == "" | is.na(date)) %>%
  select(page_number) %>%
  distinct()

#write vector to txt file
write.table(df_no_date2, "data/df_no_date2.txt", row.names = FALSE, col.names = FALSE)

```

## Verify missing texts

```{r}
#| label: verify-missing-texts

df_no_text <- df_combined %>% 
  filter(text == "" | is.na(text)) %>%
  select(page_number) %>%
  distinct()

#write vector to txt file
write.table(df_no_text, "data/df_no_text.txt", row.names = FALSE, col.names = FALSE)


```

## Quick benchmark

```{r}
#| label: quick-benchmark


benchmark_results <- microbenchmark(
  df_combined <- fread("data/combined_data_VF2.csv"),
  df_combined <- fread("data/combined_data_VF2.csv", nThread = 6),
  times = 5
)

autoplot(benchmark_results)
```


```{r}
#| label: quick-benchmark2

#| label: quick-benchmark


benchmark_results <- microbenchmark(
  df_combined <- read_csv("data/combined_data_VF2.csv"),
  df_combined <- fread("data/combined_data_VF2.csv", nThread = 12),
  times = 5
)

autoplot(benchmark_results)
```



